Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-29 awipev-CO2.Rmd

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_sf, temp_mix, temp_insitu_11m, sal_mix)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_sf) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_sf, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,ph_s_sf_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA + TA calc from sal_mix + TA reference", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)

# period 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))

@@

# period 1 also, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))

@@

# period 03, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))

@@

# period 03 also, mean of 4 previous hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))

>>>>

```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix 
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
```

@@

# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
# use the closest time to add them
closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
d$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
# create closest_datetime in d_all (copy of datetime)
d_all$closest_datetime <- d_all$datetime
d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")

# Conversion of spectro pH to insitu mix T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
pH_seafet <- pH_seafet %>%
  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))

@@

# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,ph_s_sf_temp_mix)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))

@@

```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  #dyAxis("y",valueRange = c(2000, 2650)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

@@

pco2_contros_xts <-
  dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    axis = "y2",
    "voltINT",
    label = "voltINT",
    color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(axis="y2",
    "voltEXT",
    label = "voltEXT",
    color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
   dySeries(
    "temp_insitu_ctd",
    label = "temp_insitu_ctd",
    color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
   dySeries(
    "sal_fb",
    label = "sal_fb",
    color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
   dySeries(
    "ph_s_sf_temp_mix",
    label = "ph_s_sf_temp_mix",
    color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyAxis("y2",valueRange = c(-2,2))%>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)
# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
# (2) removed from 2018-01-08 to 2018-02-02
# (3) outliers removed
# (1)
d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# (2)
d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
# (3)
d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)

#periode 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))

@@

# Periode 2, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))

@@

# period 03, mean of 4 previous hours for volt int + volt ext
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))

@@

# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))
